---
title: "Reproducibility review of: From Floorplan to Navigation Concepts: Automatic Generation
of Text-based Games"
author: "Carlos Granell \\orcid{0000-0003-1004-9695}"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  pdf_document:
    toc: false
papersize: a4
header-includes:
  - |
    % https://tex.stackexchange.com/questions/445563/ieeetran-how-to-include-orcid-in-tex-pdf-with-pdflatex/445583 (works with pdflatex)
    \usepackage{scalerel}
    \usepackage{tikz}
    \usetikzlibrary{svg.path}
    \definecolor{orcidlogocol}{HTML}{A6CE39}
    \tikzset{
      orcidlogo/.pic={
        \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
        \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                     svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z     M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                     svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
      }
    }
    \newcommand\orcid[1]{\href{https://orcid.org/#1}{\raisebox{0.15 em}{\mbox{\scalerel*{
    \begin{tikzpicture}[yscale=-1, transform shape]
    \pic{orcidlogo};
    \end{tikzpicture}
    }{|}}}}}
    \definecolor{agileblue}{RGB}{0,77,155}
urlcolor: agileblue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r logo, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', out.width='0.3\\linewidth', fig.pos='H'}
temp <- tempfile(fileext = ".pdf")
download.file(url = "https://reproducible-agile.github.io/public/images/reproducible-AGILE-logo-square.pdf", destfile = temp)
knitr::include_graphics(temp)
```

This report is part of the reproducibility review at the AGILE conference.
For more information see [https://reproducible-agile.github.io/](https://reproducible-agile.github.io/).
This document is published on OSF at OSF LINK HERE.
To cite the report use

> FULL REPORT CITATION HERE

# Reviewed paper

ADD FULL CITATION

# Summary

- Result of the reproduction
- main outcome or figure

\clearpage

# Reproducibility reviewer notes

The submission pointed to a public Git repository at <https://github.com/tomko-lab/Geometry_to_TextWorld>

## Installation

```{bash, eval=FALSE}
$ git clone https://github.com/tomko-lab/Geometry_to_TextWorld.git
```

The repository contain a README that details some instructions to set up required dependencies. Yet, the repository does not contain a license. I continue following the instructions in the README to set up the computational environment in my local machine (Ubuntu 20.04.6 LTS on WSL2 on Windows 11 Pro).


```{bash, eval=FALSE}
$ sudo apt install python3-virtualenv && virtualenv venv

$ source venv/bin/activate
```

No versions of the dependencies are provided. I use [pipreqs](https://github.com/bndr/pipreqs) package to automatically generate the `requirements.txt` file for the project based on imports detected.

```{bash, eval=FALSE}
$ pip install pipreqs

$ pipreqs .
```

As a result, the generated `requirements.txt` contains the following dependencies

```{bash, eval=FALSE}
$ cat requirements.txt
geojson==3.0.1
matplotlib==3.7.1
numpy==1.24.2
scipy==1.10.1
Shapely==2.0.1
textworld==1.5.3
```

```{bash, eval=FALSE}
$ pip install -r requirements.txt
```

The installation of the above dependencies takes aroud 20 minutes. 

However, by checking the list of dependencies in the README, the `skgeom` ([scikit-geometry](https://scikit-geometry.github.io/scikit-geometry/) package) is missing; `pipreqs` did not detect it. Therefore, it needs to be installed separately. However, as scikit-geometry cannot be installed via `pip install` (I do not use conda), I followed instructions provided in <https://wolfv.medium.com/introducing-scikit-geometry-ae1dccaad5fd>, which required to install CGAL 5.0 first and the run `python -m pip install -e . -v` from the cloned [scikit-geometry git](https://github.com/scikit-geometry/scikit-geometry) repository.

First, installation of CGAL 5.0

```{bash, eval=FALSE}
$ sudo apt-get install libcgal-dev
```

Second, I cloned the report and run the pip command.


```{bash, eval=FALSE}
$ git clone https://github.com/scikit-geometry/scikit-geometry.git

$ cd scikit-geometry

$ python -m pip install -e . -v 

```

The last instruction installs and builds sckit-geometry but it takes a while.... (20 minutes more)


```{bash, eval=FALSE}
$ pip show skgeom | grep -i version
Version: 0.1.2
```

The set up of the computational environment with pinned dependencies resulted in the following environment on my machine:

```{bash, size="tiny", eval=FALSE}
$ pip freeze
blis==0.7.9
catalogue==2.0.8
certifi==2022.12.7
cffi==1.15.1
charset-normalizer==3.1.0
click==8.1.3
cloudpickle==2.2.1
confection==0.0.4
contourpy==1.0.7
cycler==0.11.0
cymem==2.0.7
docopt==0.6.2
fonttools==4.39.3
geojson==3.0.1
gym==0.25.2
gym-notices==0.0.8
hashids==1.3.1
idna==3.4
importlib-metadata==6.3.0
importlib-resources==5.12.0
jericho==3.1.1
Jinja2==3.1.2
kiwisolver==1.4.4
langcodes==3.3.0
MarkupSafe==2.1.2
matplotlib==3.7.1
mementos==1.3.1
more-itertools==9.1.0
murmurhash==1.0.9
networkx==3.1
numpy==1.24.2
packaging==23.1
pathy==0.10.1
Pillow==9.5.0
pipreqs==0.4.13
preshed==3.0.8
prompt-toolkit==3.0.38
pybind11==2.7.1
pycparser==2.21
pydantic==1.10.7
pyparsing==3.0.9
python-dateutil==2.8.2
requests==2.28.2
scipy==1.10.1
shapely==2.0.1
six==1.16.0
-e git+https://github.com/scikit-geometry/scikit-geometry.git@71a7b2bf86e2e760f19d3b036b10da1ff89707ff#egg=skgeom
smart-open==6.3.0
spacy==3.5.2
spacy-legacy==3.0.12
spacy-loggers==1.0.4
srsly==2.4.6
TatSu==4.4.0
textworld==1.5.3
thinc==8.1.9
tqdm==4.65.0
typer==0.7.0
typing-extensions==4.5.0
urllib3==1.26.15
wasabi==1.1.1
wcwidth==0.2.6
yarg==0.1.9
zipp==3.15.0
```

## Run experiments

Authors specified in the README that the execution of the script `generator.py` is sufficient. It is unclear however what this script will produce and how the output is connected with Figure 9 of the paper, which show the results of the experiment reported.

Taking a conservative approach, I used first the simple grid environment by setting the `ENV_SIMPLE` to True in `parameters.py` (as indicated in the README).


```{bash, eval=FALSE}
$ cat parameters.py

class Parameter:
    ENV_SIMPLE = True
    DATASET_DIRECTORY = "dataset/"
    DOORS = 'doors.geojson'
    ENV = 'env.geojson'
    LANDMARKS = 'landmarks.geojson'
    GAME_ADDRESS = 'game/test_real.z8'
    MIN_DISTANCE = 1
    PLAYER = 'a1r1'

    @staticmethod
    def setScenario(isSimple=ENV_SIMPLE):
        if isSimple:
            Parameter.DATASET_DIRECTORY = "dataset/simple/"
            Parameter.GAME_ADDRESS = 'game/simple_test.z8'
            Parameter.MIN_DISTANCE = 5
            Parameter.PLAYER = 'a0r0'
```


And I ran the only script as indicated in README.

```{bash, size="tiny", eval=FALSE}
$ python generator.py

Traceback (most recent call last):
  File "generator.py", line 199, in <module>
    areas, doors, landmarks = vertex_decompose.get_info()
  File "/mnt/c/MyCode/agile2023-3535/Geometry_to_TextWorld/vertex_decompose.py", line 371, in get_info
    areas, doors, landmarks = decompose_the_floor()
  File "/mnt/c/MyCode/agile2023-3535/Geometry_to_TextWorld/vertex_decompose.py", line 364, in decompose_the_floor
    nodes[key] = decision_points_decomposition(value)
  File "/mnt/c/MyCode/agile2023-3535/Geometry_to_TextWorld/vertex_decompose.py", line 218, in decision_points_decomposition
    skeleton = sg.skeleton.create_interior_straight_skeleton(polygon)
TypeError: create_interior_straight_skeleton(): incompatible function arguments. The following argument types are supported:
    1. (arg0: CGAL::Polygon_2<CGAL::Epick, std::vector<CGAL::Point_2<CGAL::Epick>, std::allocator<CGAL::Point_2<CGAL::Epick> > > >) -> skgeom._skgeom.Skeleton
    2. (arg0: CGAL::Polygon_with_holes_2<CGAL::Epick, std::vector<CGAL::Point_2<CGAL::Epick>, std::allocator<CGAL::Point_2<CGAL::Epick> > > >) -> skgeom._skgeom.Skeleton

Invoked with: Polygon_2(
  PointC2(4.82116e+06, 7.0806e+06)
  PointC2(4.82121e+06, 7.08066e+06)
  PointC2(4.82121e+06, 7.08071e+06)
  PointC2(4.82116e+06, 7.08071e+06)
)


Did you forget to `#include <pybind11/stl.h>`? Or <pybind11/complex.h>,
<pybind11/functional.h>, <pybind11/chrono.h>, etc. Some automatic
conversions are optional and require extra headers to be included
when compiling your pybind11 module.
```


**The above code fails**. Unclear to me the reason to fail. incompatible function arguments. As an alternative, I used the real-world example (default option) by setting the `ENV_SIMPLE` to False in parameters.py

```{bash, eval=FALSE}
$ cat parameters.py

class Parameter:
    ENV_SIMPLE = False
    DATASET_DIRECTORY = "dataset/"
    DOORS = 'doors.geojson'
    ENV = 'env.geojson'
    LANDMARKS = 'landmarks.geojson'
    GAME_ADDRESS = 'game/test_real.z8'
    MIN_DISTANCE = 1
    PLAYER = 'a1r1'

    @staticmethod
    def setScenario(isSimple=ENV_SIMPLE):
        if isSimple:
            Parameter.DATASET_DIRECTORY = "dataset/simple/"
            Parameter.GAME_ADDRESS = 'game/simple_test.z8'
            Parameter.MIN_DISTANCE = 5
            Parameter.PLAYER = 'a0r0'
```

I ran again the script and **produced the same error**.

```{bash, size="tiny", eval=FALSE}
$ python generator.py

Traceback (most recent call last):
  File "generator.py", line 199, in <module>
    areas, doors, landmarks = vertex_decompose.get_info()
  File "/mnt/c/MyCode/agile2023-3535/Geometry_to_TextWorld/vertex_decompose.py", line 371, in get_info
    areas, doors, landmarks = decompose_the_floor()
  File "/mnt/c/MyCode/agile2023-3535/Geometry_to_TextWorld/vertex_decompose.py", line 364, in decompose_the_floor
    nodes[key] = decision_points_decomposition(value)
  File "/mnt/c/MyCode/agile2023-3535/Geometry_to_TextWorld/vertex_decompose.py", line 218, in decision_points_decomposition
    skeleton = sg.skeleton.create_interior_straight_skeleton(polygon)
TypeError: create_interior_straight_skeleton(): incompatible function arguments. The following argument types are supported:
    1. (arg0: CGAL::Polygon_2<CGAL::Epick, std::vector<CGAL::Point_2<CGAL::Epick>, std::allocator<CGAL::Point_2<CGAL::Epick> > > >) -> skgeom._skgeom.Skeleton
    2. (arg0: CGAL::Polygon_with_holes_2<CGAL::Epick, std::vector<CGAL::Point_2<CGAL::Epick>, std::allocator<CGAL::Point_2<CGAL::Epick> > > >) -> skgeom._skgeom.Skeleton

Invoked with: Polygon_2(
  PointC2(4.82116e+06, 7.0806e+06)
  PointC2(4.82121e+06, 7.08066e+06)
  PointC2(4.82121e+06, 7.08071e+06)
  PointC2(4.82116e+06, 7.08071e+06)
)


Did you forget to `#include <pybind11/stl.h>`? Or <pybind11/complex.h>,
<pybind11/functional.h>, <pybind11/chrono.h>, etc. Some automatic
conversions are optional and require extra headers to be included
when compiling your pybind11 module.
```

## Recommnedations

- Provide a `requirements.txt` and make sure to pin the computing environment so that the `requirements.txt` contains the actual versions you use(d).
- In your github repository, please specify a licence.
- In your README, please specify estimate time for computing environmental installation. 
- For reproducibility evaluation (and possibly also demonstration), it would be great if you explain what the script produces and how the expected output is connected with the reported demonstration (section 5) in the paper. Should we expect a kind of floorplan graph as in Figure 9? Or should we expect an interactive session as in Table 4? 


<!--
- technical details about reproduction
- code snippets
- summary of communication with author
- figures/screenshots
- runtime
- reproduction efforts
-->



```{r, echo=FALSE, eval=FALSE, results='hide'}
# create ZIP of reproduction files and upload to OSF
library("zip")
library("here")

zipfile <- here::here("PATH/agile-reproreview-YEAR-NUMBER.zip")
file.remove(zipfile)
zip::zipr(zipfile,
          here::here("2020-018/files to add to the zip, if any"))

library("osfr") # See docs at https://docs.ropensci.org/osfr/
# OSF_PAT is in .Renviron in parent directory
# We cannot use osfr to create a new component (with osfr::osf_create_component(x = osfr::osf_retrieve_node("6k5fh"), ...) because that will set the storage location to outside Europe.

# retrieve project
project <- osfr::osf_retrieve_node("OSF ID")

# upload files
osfr::osf_upload(x = project,
                 conflicts = "overwrite",
                 path = c(list.files(here::here("PATH"),
                                     pattern = "agile-reproreview-.*(pdf$|Rmd$|zip$)",
                                     full.names = TRUE),
                          "COPYRIGHT"
                          )
                 )
```